Sketch of DP - Bayesian Inference

### 2018-07-17 main-sketch.tex
section 3 finished

This mechanism also extends to the Dirichlet-Multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
\[
  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\betaf(\valpha_1) \betaf(\valpha_2)}},
\]
and by replacing the $\betaset$ with set of posterior Dirichlet distributions candidates. Also, the smooth sensitivity $S(x)$ in (\ref{eq:smooth}) will be
computed by letting $\dataobs'$ range over all the elements in $\datauni^{n}$ adjacent to $\dataobs$.
Notice that $\betaset$ has $\binom{n + 1}{m - 1}$ elements in this case. We will denote by
$\hexpmechd$ the mechanism for the Dirichlet-Multinomial system.
% In what follows, we will use a correspondence between the probability
%  $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
%  $r\in\betaset$ and the probability 
%  $\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
%  \hlg(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
%  $r\in\betaset$ we have:
% $$
% \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
% \frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
%  \hlg(\bysinfer(x),r)]\Big )
% $$
% To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hlg(\bysinfer(x),r)$, i.e., $u(x,z)$. We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$. We assume the number of candidates $z \in \mathcal{R}$ that satisfy $u(z,x) = u(r,x)$ is $|r|$, we have  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |r| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. Because Hellinger distance  $\hlg(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis. It can be infer that $|z| = 2$ for any candidates, apart from the true output, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. This parameter can be eliminate in both sides in proof.

>>>>

This mechanism also extends to the Dirichlet-Multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
\[
  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\betaf(\valpha_1) \betaf(\valpha_2)}},
\]
and by replacing the $\betaset$ with set of posterior Dirichlet distributions candidates. Also, the smooth sensitivity $S(\dataobs)$ in (\ref{eq:smooth}) will be
computed by letting $\dataobs'$ range over all the elements in $\datauni^{n}$ adjacent to $\dataobs$.
Notice that $\betaset$ has $\binom{n + 1}{m - 1}$ elements in this case. We will denote by
$\hexpmechd$ the mechanism for the Dirichlet-Multinomial system.
% In what follows, we will use a correspondence between the probability
%  $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
%  $r\in\betaset$ and the probability 
%  $\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
%  \hlg(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
%  $r\in\betaset$ we have:
% $$
% \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
% \frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
%  \hlg(\bysinfer(x),r)]\Big )
% $$
% To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hlg(\bysinfer(x),r)$, i.e., $u(x,z)$. We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$. We assume the number of candidates $z \in \mathcal{R}$ that satisfy $u(z,x) = u(r,x)$ is $|r|$, we have  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |r| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. Because Hellinger distance  $\hlg(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis. It can be infer that $|z| = 2$ for any candidates, apart from the true output, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. This parameter can be eliminate in both sides in proof.
